---
title: "/r/anime Seasonal Spending"
description: |
  How much does /r/anime spend per season?
author:
  - name: its-gazza
    url: {}
date: 12-09-2020
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  chunk_output_type: console
draft: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This post will look at how much does [/r/anime](https://www.reddit.com/r/anime/)
spend per season in the past two years.

## Getting the data
In order to get the data I use [praw](https://praw.readthedocs.io/en/latest/) 
for Python to do the following in [reddit_api.py](./reddit_api.py):  

* From [holo/season_configs](https://github.com/r-anime/holo/tree/master/season_configs)
download each seasons yaml
* Loop through each title and use `.search()` to get all episode info
* Store episode info under dataframe `output`
* Write result as csv

## Load data
Now that I've explained how to get the data, we'll read in the data  

```{r Read data}
library(tidyverse)
library(readr)
library(here)
library(knitr)
library(scales)

df <- read_csv('./output.csv')

head(df) %>% 
  kable()
```

## Aggregating by season
Now we'll look at how much /r/anime spend per season  

```{r}
df %>% 
  group_by(year, season) %>%
  summarise(total_karma = sum(karma),
            total_coins = sum(coins),
            total_titles = sum(n_distinct(title))) %>%
  mutate(year = as.character(year)) %>% 
  ggplot(aes(x = season, y = total_coins, col = year)) + 
  geom_point(size = 3) + 
  scale_y_continuous(labels = comma) + 
  labs(title = "/r/anime Spend per season",
       x = "Season",
       y = "Total Coins Spend",
       col = "Year")
```

## Aggregate by show

```{r}
df %>% 
  group_by(title) %>% 
  summarise(total_karma = sum(karma),
            total_coins = sum(coins),
            episodes = n()) %>%
  arrange(total_karma %>% desc)
```


